### 2016-11-11 llncsmain.tex
initial commit

% This is LLNCS.DEM the demonstration file of
% the LaTeX macro package from Springer-Verlag
% for Lecture Notes in Computer Science,
% version 2.4 for LaTeX2e as of 16. April 2010
%
 % additional mark in the TOC
%

\chapter*{Organization}
ECOOP'95 is organized by the department of Computer Science, Univeristy
of \AA rhus and AITO (association Internationa pour les Technologie
Object) in cooperation with ACM/SIGPLAN.
%
\section*{Executive Commitee}
\begin{tabular}{@{}p{5cm}@{}p{7.2cm}@{}}
Conference Chair:&Ole Lehrmann Madsen (\AA rhus University, DK)\\
Program Chair:   &Walter Olthoff (DFKI GmbH, Germany)\\
Organizing Chair:&J\o rgen Lindskov Knudsen (\AA rhus University, DK)\\
Tutorials:&Birger M\o ller-Pedersen\hfil\break
(Norwegian Computing Center, Norway)\\
Workshops:&Eric Jul (University of Kopenhagen, Denmark)\\
Panels:&Boris Magnusson (Lund University, Sweden)\\
Exhibition:&Elmer Sandvad (\AA rhus University, DK)\\
Demonstrations:&Kurt N\o rdmark (\AA rhus University, DK)
\end{tabular}
%
\section*{Program Commitee}
\begin{tabular}{@{}p{5cm}@{}p{7.2cm}@{}}
Conference Chair:&Ole Lehrmann Madsen (\AA rhus University, DK)\\
Program Chair:   &Walter Olthoff (DFKI GmbH, Germany)\\
Organizing Chair:&J\o rgen Lindskov Knudsen (\AA rhus University, DK)\\
Tutorials:&Birger M\o ller-Pedersen\hfil\break
(Norwegian Computing Center, Norway)\\
Workshops:&Eric Jul (University of Kopenhagen, Denmark)\\
Panels:&Boris Magnusson (Lund University, Sweden)\\
Exhibition:&Elmer Sandvad (\AA rhus University, DK)\\
Demonstrations:&Kurt N\o rdmark (\AA rhus University, DK)
\end{tabular}
%
\begin{multicols}{3}[\section*{Referees}]
V.~Andreev\\
B\"arwolff\\
E.~Barrelet\\
H.P.~Beck\\
G.~Bernardi\\
E.~Binder\\
P.C.~Bosetti\\
Braunschweig\\
F.W.~B\"usser\\
T.~Carli\\
A.B.~Clegg\\
G.~Cozzika\\
S.~Dagoret\\
Del~Buono\\
P.~Dingus\\
H.~Duhm\\
J.~Ebert\\
S.~Eichenberger\\
R.J.~Ellison\\
Feltesse\\
W.~Flauger\\
A.~Fomenko\\
G.~Franke\\
J.~Garvey\\
M.~Gennis\\
L.~Goerlich\\
P.~Goritchev\\
H.~Greif\\
E.M.~Hanlon\\
R.~Haydar\\
R.C.W.~Henderso\\
P.~Hill\\
H.~Hufnagel\\
A.~Jacholkowska\\
Johannsen\\
S.~Kasarian\\
I.R.~Kenyon\\
C.~Kleinwort\\
T.~K\"ohler\\
S.D.~Kolya\\
P.~Kostka\\
U.~Kr\"uger\\
J.~Kurzh\"ofer\\
M.P.J.~Landon\\
A.~Lebedev\\
Ch.~Ley\\
F.~Linsel\\
H.~Lohmand\\
Martin\\
S.~Masson\\
K.~Meier\\
C.A.~Meyer\\
S.~Mikocki\\
J.V.~Morris\\
B.~Naroska\\
Nguyen\\
U.~Obrock\\
G.D.~Patel\\
Ch.~Pichler\\
S.~Prell\\
F.~Raupach\\
V.~Riech\\
P.~Robmann\\
N.~Sahlmann\\
P.~Schleper\\
Sch\"oning\\
B.~Schwab\\
A.~Semenov\\
G.~Siegmon\\
J.R.~Smith\\
M.~Steenbock\\
U.~Straumann\\
C.~Thiebaux\\
P.~Van~Esch\\
from Yerevan Ph\\
L.R.~West\\
G.-G.~Winter\\
T.P.~Yiou\\
M.~Zimmer\end{multicols}
%
\section*{Sponsoring Institutions}
%
Bernauer-Budiman Inc., Reading, Mass.\\
The Hofmann-International Company, San Louis Obispo, Cal.\\
Kramer Industries, Heidelberg, Germany
%
\tableofcontents
%
\mainmatter              % start of the contributions
%
\title{Hamiltonian Mechanics unter besonderer Ber\"ucksichtigung der
h\"ohreren Lehranstalten}
%
\titlerunning{Hamiltonian Mechanics}  % abbreviated title (for running head)
%                                     also used for the TOC unless
%                                     \toctitle is used
%
\author{Ivar Ekeland\inst{1} \and Roger Temam\inst{2}
Jeffrey Dean \and David Grove \and Craig Chambers \and Kim~B.~Bruce \and
Elsa Bertino}
%
\authorrunning{Ivar Ekeland et al.} % abbreviated author list (for running head)
%
%%%% list of authors for the TOC (use if author list has to be modified)
\tocauthor{Ivar Ekeland, Roger Temam, Jeffrey Dean, David Grove,
Craig Chambers, Kim B. Bruce, and Elisa Bertino}
%
\institute{Princeton University, Princeton NJ 08544, USA,\\
\email{I.Ekeland@princeton.edu},\\ WWW home page:
\texttt{http://users/\homedir iekeland/web/welcome.html}
\and
Universit\'{e} de Paris-Sud,
Laboratoire d'Analyse Num\'{e}rique, B\^{a}timent 425,\\
F-91405 Orsay Cedex, France}

\maketitle              % typeset the title of the contribution

\begin{abstract}
The abstract should summarize the contents of the paper
using at least 70 and at most 150 words. It will be set in 9-point
font size and be inset 1.0 cm from the right and left margins.
There will be two blank lines before and after the Abstract. \dots
\keywords{computational geometry, graph theory, Hamilton cycles}
\end{abstract}
%
\section{Fixed-Period Problems: The Sublinear Case}
%
With this chapter, the preliminaries are over, and we begin the search
for periodic solutions to Hamiltonian systems. All this will be done in
the convex case; that is, we shall study the boundary-value problem
\begin{eqnarray*}
  \dot{x}&=&JH' (t,x)\\
  x(0) &=& x(T)
\end{eqnarray*}
with $H(t,\cdot)$ a convex function of $x$, going to $+\infty$ when
$\left\|x\right\| \to \infty$.

%
\subsection{Autonomous Systems}
%
In this section, we will consider the case when the Hamiltonian $H(x)$
is autonomous. For the sake of simplicity, we shall also assume that it
is $C^{1}$.

We shall first consider the question of nontriviality, within the
general framework of
$\left(A_{\infty},B_{\infty}\right)$-subquadratic Hamiltonians. In
the second subsection, we shall look into the special case when $H$ is
$\left(0,b_{\infty}\right)$-subquadratic,
and we shall try to derive additional information.
%
\subsubsection{The General Case: Nontriviality.}
%
We assume that $H$ is
$\left(A_{\infty},B_{\infty}\right)$-sub\-qua\-dra\-tic at infinity,
for some constant symmetric matrices $A_{\infty}$ and $B_{\infty}$,
with $B_{\infty}-A_{\infty}$ positive definite. Set:
\begin{eqnarray}
\gamma :&=&{\rm smallest\ eigenvalue\ of}\ \ B_{\infty} - A_{\infty} \\
  \lambda : &=& {\rm largest\ negative\ eigenvalue\ of}\ \
  J \frac{d}{dt} +A_{\infty}\ .
\end{eqnarray}

Theorem~\ref{ghou:pre} tells us that if $\lambda +\gamma < 0$, the
boundary-value problem:
\begin{equation}
\begin{array}{rcl}
  \dot{x}&=&JH' (x)\\
  x(0)&=&x (T)
\end{array}
\end{equation}
has at least one solution
$\overline{x}$, which is found by minimizing the dual
action functional:
\begin{equation}
  \psi (u) = \int_{o}^{T} \left[\frac{1}{2}
  \left(\Lambda_{o}^{-1} u,u\right) + N^{\ast} (-u)\right] dt
\end{equation}
on the range of $\Lambda$, which is a subspace $R (\Lambda)_{L}^{2}$
with finite codimension. Here
\begin{equation}
  N(x) := H(x) - \frac{1}{2} \left(A_{\infty} x,x\right)
\end{equation}
is a convex function, and
\begin{equation}
  N(x) \le \frac{1}{2}
  \left(\left(B_{\infty} - A_{\infty}\right) x,x\right)
  + c\ \ \ \forall x\ .
\end{equation}

%
\begin{proposition}
Assume $H'(0)=0$ and $ H(0)=0$. Set:
\begin{equation}
  \delta := \liminf_{x\to 0} 2 N (x) \left\|x\right\|^{-2}\ .
  \label{eq:one}
\end{equation}

If $\gamma < - \lambda < \delta$,
the solution $\overline{u}$ is non-zero:
\begin{equation}
  \overline{x} (t) \ne 0\ \ \ \forall t\ .
\end{equation}
\end{proposition}
%
\begin{proof}
Condition (\ref{eq:one}) means that, for every
$\delta ' > \delta$, there is some $\varepsilon > 0$ such that
\begin{equation}
  \left\|x\right\| \le \varepsilon \Rightarrow N (x) \le
  \frac{\delta '}{2} \left\|x\right\|^{2}\ .
\end{equation}

It is an exercise in convex analysis, into which we shall not go, to
show that this implies that there is an $\eta > 0$ such that
\begin{equation}
  f\left\|x\right\| \le \eta
  \Rightarrow N^{\ast} (y) \le \frac{1}{2\delta '}
  \left\|y\right\|^{2}\ .
  \label{eq:two}
\end{equation}

\begin{figure}
\vspace{2.5cm}
\caption{This is the caption of the figure displaying a white eagle and
a white horse on a snow field}
\end{figure}

Since $u_{1}$ is a smooth function, we will have
$\left\|hu_{1}\right\|_\infty \le \eta$
for $h$ small enough, and inequality (\ref{eq:two}) will hold,
yielding thereby:
\begin{equation}
  \psi (hu_{1}) \le \frac{h^{2}}{2}
  \frac{1}{\lambda} \left\|u_{1} \right\|_{2}^{2} + \frac{h^{2}}{2}
  \frac{1}{\delta '} \left\|u_{1}\right\|^{2}\ .
\end{equation}

If we choose $\delta '$ close enough to $\delta$, the quantity
$\left(\frac{1}{\lambda} + \frac{1}{\delta '}\right)$
will be negative, and we end up with
\begin{equation}
  \psi (hu_{1}) < 0\ \ \ \ \ {\rm for}\ \ h\ne 0\ \ {\rm small}\ .
\end{equation}

On the other hand, we check directly that $\psi (0) = 0$. This shows
that 0 cannot be a minimizer of $\psi$, not even a local one.
So $\overline{u} \ne 0$ and
$\overline{u} \ne \Lambda_{o}^{-1} (0) = 0$. \qed
\end{proof}
%
\begin{corollary}
Assume $H$ is $C^{2}$ and
$\left(a_{\infty},b_{\infty}\right)$-subquadratic at infinity. Let
$\xi_{1},\allowbreak\dots,\allowbreak\xi_{N}$  be the
equilibria, that is, the solutions of $H' (\xi ) = 0$.
Denote by $\omega_{k}$
the smallest eigenvalue of $H'' \left(\xi_{k}\right)$, and set:
\begin{equation}
  \omega : = {\rm Min\,} \left\{\omega_{1},\dots,\omega_{k}\right\}\ .
\end{equation}
If:
\begin{equation}
  \frac{T}{2\pi} b_{\infty} <
  - E \left[- \frac{T}{2\pi}a_{\infty}\right] <
  \frac{T}{2\pi}\omega
  \label{eq:three}
\end{equation}
then minimization of $\psi$ yields a non-constant $T$-periodic solution
$\overline{x}$.
\end{corollary}
%

We recall once more that by the integer part $E [\alpha ]$ of
$\alpha \in \bbbr$, we mean the $a\in \bbbz$
such that $a< \alpha \le a+1$. For instance,
if we take $a_{\infty} = 0$, Corollary 2 tells
us that $\overline{x}$ exists and is
non-constant provided that:

\begin{equation}
  \frac{T}{2\pi} b_{\infty} < 1 < \frac{T}{2\pi}
\end{equation}
or
\begin{equation}
  T\in \left(\frac{2\pi}{\omega},\frac{2\pi}{b_{\infty}}\right)\ .
  \label{eq:four}
\end{equation}

%
\begin{proof}
The spectrum of $\Lambda$ is $\frac{2\pi}{T} \bbbz +a_{\infty}$. The
largest negative eigenvalue $\lambda$ is given by
$\frac{2\pi}{T}k_{o} +a_{\infty}$,
where
\begin{equation}
  \frac{2\pi}{T}k_{o} + a_{\infty} < 0
  \le \frac{2\pi}{T} (k_{o} +1) + a_{\infty}\ .
\end{equation}
Hence:
\begin{equation}
  k_{o} = E \left[- \frac{T}{2\pi} a_{\infty}\right] \ .
\end{equation}

The condition $\gamma < -\lambda < \delta$ now becomes:
\begin{equation}
  b_{\infty} - a_{\infty} <
  - \frac{2\pi}{T} k_{o} -a_{\infty} < \omega -a_{\infty}
\end{equation}
which is precisely condition (\ref{eq:three}).\qed
\end{proof}
%

\begin{lemma}
Assume that $H$ is $C^{2}$ on $\bbbr^{2n} \setminus \{ 0\}$ and
that $H'' (x)$ is non-de\-gen\-er\-ate for any $x\ne 0$. Then any local
minimizer $\widetilde{x}$ of $\psi$ has minimal period $T$.
\end{lemma}
%
\begin{proof}
We know that $\widetilde{x}$, or
$\widetilde{x} + \xi$ for some constant $\xi
\in \bbbr^{2n}$, is a $T$-periodic solution of the Hamiltonian system:
\begin{equation}
  \dot{x} = JH' (x)\ .
\end{equation}

There is no loss of generality in taking $\xi = 0$. So
$\psi (x) \ge \psi (\widetilde{x} )$
for all $\widetilde{x}$ in some neighbourhood of $x$ in
$W^{1,2} \left(\bbbr / T\bbbz ; \bbbr^{2n}\right)$.

But this index is precisely the index
$i_{T} (\widetilde{x} )$ of the $T$-periodic
solution $\widetilde{x}$ over the interval
$(0,T)$, as defined in Sect.~2.6. So
\begin{equation}
  i_{T} (\widetilde{x} ) = 0\ .
  \label{eq:five}
\end{equation}

Now if $\widetilde{x}$ has a lower period, $T/k$ say,
we would have, by Corollary 31:
\begin{equation}
  i_{T} (\widetilde{x} ) =
  i_{kT/k}(\widetilde{x} ) \ge
  ki_{T/k} (\widetilde{x} ) + k-1 \ge k-1 \ge 1\ .
\end{equation}

This would contradict (\ref{eq:five}), and thus cannot happen.\qed
\end{proof}
%
\paragraph{Notes and Comments.}
The results in this section are a
refined version of \cite{clar:eke};
the minimality result of Proposition
14 was the first of its kind.

To understand the nontriviality conditions, such as the one in formula
(\ref{eq:four}), one may think of a one-parameter family
$x_{T}$, $T\in \left(2\pi\omega^{-1}, 2\pi b_{\infty}^{-1}\right)$
of periodic solutions, $x_{T} (0) = x_{T} (T)$,
with $x_{T}$ going away to infinity when $T\to 2\pi \omega^{-1}$,
which is the period of the linearized system at 0.

\begin{table}
\caption{This is the example table taken out of {\it The
\TeX{}book,} p.\,246}
\begin{center}
\begin{tabular}{r@{\quad}rl}
\hline
\multicolumn{1}{l}{\rule{0pt}{12pt}
                   Year}&\multicolumn{2}{l}{World population}\\[2pt]
\hline\rule{0pt}{12pt}
8000 B.C.  &     5,000,000& \\
  50 A.D.  &   200,000,000& \\
1650 A.D.  &   500,000,000& \\
1945 A.D.  & 2,300,000,000& \\
1980 A.D.  & 4,400,000,000& \\[2pt]
\hline
\end{tabular}
\end{center}
\end{table}
%
\begin{theorem} [Ghoussoub-Preiss]\label{ghou:pre}
Assume $H(t,x)$ is
$(0,\varepsilon )$-subquadratic at
infinity for all $\varepsilon > 0$, and $T$-periodic in $t$
\begin{equation}
  H (t,\cdot )\ \ \ \ \ {\rm is\ convex}\ \ \forall t
\end{equation}
\begin{equation}
  H (\cdot ,x)\ \ \ \ \ {\rm is}\ \ T{\rm -periodic}\ \ \forall x
\end{equation}
\begin{equation}
  H (t,x)\ge n\left(\left\|x\right\|\right)\ \ \ \ \
  {\rm with}\ \ n (s)s^{-1}\to \infty\ \ {\rm as}\ \ s\to \infty
\end{equation}
\begin{equation}
  \forall \varepsilon > 0\ ,\ \ \ \exists c\ :\
  H(t,x) \le \frac{\varepsilon}{2}\left\|x\right\|^{2} + c\ .
\end{equation}

Assume also that $H$ is $C^{2}$, and $H'' (t,x)$ is positive definite
everywhere. Then there is a sequence $x_{k}$, $k\in \bbbn$, of
$kT$-periodic solutions of the system
\begin{equation}
  \dot{x} = JH' (t,x)
\end{equation}
such that, for every $k\in \bbbn$, there is some $p_{o}\in\bbbn$ with:
\begin{equation}
  p\ge p_{o}\Rightarrow x_{pk} \ne x_{k}\ .
\end{equation}
\qed
\end{theorem}
%
\begin{example} [{{\rm External forcing}}]
Consider the system:
\begin{equation}
  \dot{x} = JH' (x) + f(t)
\end{equation}
where the Hamiltonian $H$ is
$\left(0,b_{\infty}\right)$-subquadratic, and the
forcing term is a distribution on the circle:
\begin{equation}
  f = \frac{d}{dt} F + f_{o}\ \ \ \ \
  {\rm with}\ \ F\in L^{2} \left(\bbbr / T\bbbz; \bbbr^{2n}\right)\ ,
\end{equation}
where $f_{o} : = T^{-1}\int_{o}^{T} f (t) dt$. For instance,
\begin{equation}
  f (t) = \sum_{k\in \bbbn} \delta_{k} \xi\ ,
\end{equation}
where $\delta_{k}$ is the Dirac mass at $t= k$ and
$\xi \in \bbbr^{2n}$ is a
constant, fits the prescription. This means that the system
$\dot{x} = JH' (x)$ is being excited by a
series of identical shocks at interval $T$.
\end{example}
%
\begin{definition}
Let $A_{\infty} (t)$ and $B_{\infty} (t)$ be symmetric
operators in $\bbbr^{2n}$, depending continuously on
$t\in [0,T]$, such that
$A_{\infty} (t) \le B_{\infty} (t)$ for all $t$.

A Borelian function
$H: [0,T]\times \bbbr^{2n} \to \bbbr$
is called
$\left(A_{\infty} ,B_{\infty}\right)$-{\it subquadratic at infinity}
if there exists a function $N(t,x)$ such that:
\begin{equation}
  H (t,x) = \frac{1}{2} \left(A_{\infty} (t) x,x\right) + N(t,x)
\end{equation}
\begin{equation}
  \forall t\ ,\ \ \ N(t,x)\ \ \ \ \
  {\rm is\ convex\ with\  respect\  to}\ \ x
\end{equation}
\begin{equation}
  N(t,x) \ge n\left(\left\|x\right\|\right)\ \ \ \ \
  {\rm with}\ \ n(s)s^{-1}\to +\infty\ \ {\rm as}\ \ s\to +\infty
\end{equation}
\begin{equation}
  \exists c\in \bbbr\ :\ \ \ H (t,x) \le
  \frac{1}{2} \left(B_{\infty} (t) x,x\right) + c\ \ \ \forall x\ .
\end{equation}

If $A_{\infty} (t) = a_{\infty} I$ and
$B_{\infty} (t) = b_{\infty} I$, with
$a_{\infty} \le b_{\infty} \in \bbbr$,
we shall say that $H$ is
$\left(a_{\infty},b_{\infty}\right)$-subquadratic
at infinity. As an example, the function
$\left\|x\right\|^{\alpha}$, with
$1\le \alpha < 2$, is $(0,\varepsilon )$-subquadratic at infinity
for every $\varepsilon > 0$. Similarly, the Hamiltonian
\begin{equation}
H (t,x) = \frac{1}{2} k \left\|k\right\|^{2} +\left\|x\right\|^{\alpha}
\end{equation}
is $(k,k+\varepsilon )$-subquadratic for every $\varepsilon > 0$.
Note that, if $k<0$, it is not convex.
\end{definition}
%

\paragraph{Notes and Comments.}
The first results on subharmonics were
obtained by Rabinowitz in \cite{rab}, who showed the existence of
infinitely many subharmonics both in the subquadratic and superquadratic
case, with suitable growth conditions on $H'$. Again the duality
approach enabled Clarke and Ekeland in \cite{clar:eke:2} to treat the
same problem in the convex-subquadratic case, with growth conditions on
$H$ only.

Recently, Michalek and Tarantello (see \cite{mich:tar} and \cite{tar})
have obtained lower bound on the number of subharmonics of period $kT$,
based on symmetry considerations and on pinching estimates, as in
Sect.~5.2 of this article.

%
% ---- Bibliography ----
%
\begin{thebibliography}{5}
%
\bibitem {clar:eke}
Clarke, F., Ekeland, I.:
Nonlinear oscillations and
boundary-value problems for Hamiltonian systems.
Arch. Rat. Mech. Anal. 78, 315--333 (1982)

\bibitem {clar:eke:2}
Clarke, F., Ekeland, I.:
Solutions p\'{e}riodiques, du
p\'{e}riode donn\'{e}e, des \'{e}quations hamiltoniennes.
Note CRAS Paris 287, 1013--1015 (1978)

\bibitem {mich:tar}
Michalek, R., Tarantello, G.:
Subharmonic solutions with prescribed minimal
period for nonautonomous Hamiltonian systems.
J. Diff. Eq. 72, 28--55 (1988)

\bibitem {tar}
Tarantello, G.:
Subharmonic solutions for Hamiltonian
systems via a $\bbbz_{p}$ pseudoindex theory.
Annali di Matematica Pura (to appear)

\bibitem {rab}
Rabinowitz, P.:
On subharmonic solutions of a Hamiltonian system.
Comm. Pure Appl. Math. 33, 609--633 (1980)

\end{thebibliography}

%
% second contribution with nearly identical text,
% slightly changed contribution head (all entries
% appear as defaults), and modified bibliography
%
\title{Hamiltonian Mechanics2}

\author{Ivar Ekeland\inst{1} \and Roger Temam\inst{2}}

\institute{Princeton University, Princeton NJ 08544, USA
\and
Universit\'{e} de Paris-Sud,
Laboratoire d'Analyse Num\'{e}rique, B\^{a}timent 425,\\
F-91405 Orsay Cedex, France}

\maketitle
%
% Modify the bibliography environment to call for the author-year
% system. This is done normally with the citeauthoryear option
% for a particular contribution.
\makeatletter
\renewenvironment{thebibliography}[1]
     {\section*{\refname}
      \small
      \list{}%
           {\settowidth\labelwidth{}%
            \leftmargin\parindent
            \itemindent=-\parindent
            \labelsep=\z@
            \if@openbib
              \advance\leftmargin\bibindent
              \itemindent -\bibindent
              \listparindent \itemindent
              \parsep \z@
            \fi
            \usecounter{enumiv}%
            \let\p@enumiv\@empty
            \renewcommand\theenumiv{}}%
      \if@openbib
        \renewcommand\newblock{\par}%
      \else
        \renewcommand\newblock{\hskip .11em \@plus.33em \@minus.07em}%
      \fi
      \sloppy\clubpenalty4000\widowpenalty4000%
      \sfcode`\.=\@m}
     {\def\@noitemerr
       {\@latex@warning{Empty `thebibliography' environment}}%
      \endlist}
      \def\@cite#1{#1}%
      \def\@lbibitem[#1]#2{\item[]\if@filesw
        {\def\protect##1{\string ##1\space}\immediate
      \write\@auxout{\string\bibcite{#2}{#1}}}\fi\ignorespaces}
\makeatother
%
\begin{abstract}
The abstract should summarize the contents of the paper
using at least 70 and at most 150 words. It will be set in 9-point
font size and be inset 1.0 cm from the right and left margins.
There will be two blank lines before and after the Abstract. \dots
\keywords{graph transformations, convex geometry, lattice computations,
convex polygons, triangulations, discrete geometry}
\end{abstract}
%
\section{Fixed-Period Problems: The Sublinear Case}
%
With this chapter, the preliminaries are over, and we begin the search
for periodic solutions to Hamiltonian systems. All this will be done in
the convex case; that is, we shall study the boundary-value problem
\begin{eqnarray*}
  \dot{x}&=&JH' (t,x)\\
  x(0) &=& x(T)
\end{eqnarray*}
with $H(t,\cdot)$ a convex function of $x$, going to $+\infty$ when
$\left\|x\right\| \to \infty$.

%
\subsection{Autonomous Systems}
%
In this section, we will consider the case when the Hamiltonian $H(x)$
is autonomous. For the sake of simplicity, we shall also assume that it
is $C^{1}$.

We shall first consider the question of nontriviality, within the
general framework of
$\left(A_{\infty},B_{\infty}\right)$-subquadratic Hamiltonians. In
the second subsection, we shall look into the special case when $H$ is
$\left(0,b_{\infty}\right)$-subquadratic,
and we shall try to derive additional information.
%
\subsubsection{The General Case: Nontriviality.}
%
We assume that $H$ is
$\left(A_{\infty},B_{\infty}\right)$-sub\-qua\-dra\-tic at infinity,
for some constant symmetric matrices $A_{\infty}$ and $B_{\infty}$,
with $B_{\infty}-A_{\infty}$ positive definite. Set:
\begin{eqnarray}
\gamma :&=&{\rm smallest\ eigenvalue\ of}\ \ B_{\infty} - A_{\infty} \\
  \lambda : &=& {\rm largest\ negative\ eigenvalue\ of}\ \
  J \frac{d}{dt} +A_{\infty}\ .
\end{eqnarray}

Theorem 21 tells us that if $\lambda +\gamma < 0$, the boundary-value
problem:
\begin{equation}
\begin{array}{rcl}
  \dot{x}&=&JH' (x)\\
  x(0)&=&x (T)
\end{array}
\end{equation}
has at least one solution
$\overline{x}$, which is found by minimizing the dual
action functional:
\begin{equation}
  \psi (u) = \int_{o}^{T} \left[\frac{1}{2}
  \left(\Lambda_{o}^{-1} u,u\right) + N^{\ast} (-u)\right] dt
\end{equation}
on the range of $\Lambda$, which is a subspace $R (\Lambda)_{L}^{2}$
with finite codimension. Here
\begin{equation}
  N(x) := H(x) - \frac{1}{2} \left(A_{\infty} x,x\right)
\end{equation}
is a convex function, and
\begin{equation}
  N(x) \le \frac{1}{2}
  \left(\left(B_{\infty} - A_{\infty}\right) x,x\right)
  + c\ \ \ \forall x\ .
\end{equation}

%
\begin{proposition}
Assume $H'(0)=0$ and $ H(0)=0$. Set:
\begin{equation}
  \delta := \liminf_{x\to 0} 2 N (x) \left\|x\right\|^{-2}\ .
  \label{2eq:one}
\end{equation}

If $\gamma < - \lambda < \delta$,
the solution $\overline{u}$ is non-zero:
\begin{equation}
  \overline{x} (t) \ne 0\ \ \ \forall t\ .
\end{equation}
\end{proposition}
%
\begin{proof}
Condition (\ref{2eq:one}) means that, for every
$\delta ' > \delta$, there is some $\varepsilon > 0$ such that
\begin{equation}
  \left\|x\right\| \le \varepsilon \Rightarrow N (x) \le
  \frac{\delta '}{2} \left\|x\right\|^{2}\ .
\end{equation}

It is an exercise in convex analysis, into which we shall not go, to
show that this implies that there is an $\eta > 0$ such that
\begin{equation}
  f\left\|x\right\| \le \eta
  \Rightarrow N^{\ast} (y) \le \frac{1}{2\delta '}
  \left\|y\right\|^{2}\ .
  \label{2eq:two}
\end{equation}

\begin{figure}
\vspace{2.5cm}
\caption{This is the caption of the figure displaying a white eagle and
a white horse on a snow field}
\end{figure}

Since $u_{1}$ is a smooth function, we will have
$\left\|hu_{1}\right\|_\infty \le \eta$
for $h$ small enough, and inequality (\ref{2eq:two}) will hold,
yielding thereby:
\begin{equation}
  \psi (hu_{1}) \le \frac{h^{2}}{2}
  \frac{1}{\lambda} \left\|u_{1} \right\|_{2}^{2} + \frac{h^{2}}{2}
  \frac{1}{\delta '} \left\|u_{1}\right\|^{2}\ .
\end{equation}

If we choose $\delta '$ close enough to $\delta$, the quantity
$\left(\frac{1}{\lambda} + \frac{1}{\delta '}\right)$
will be negative, and we end up with
\begin{equation}
  \psi (hu_{1}) < 0\ \ \ \ \ {\rm for}\ \ h\ne 0\ \ {\rm small}\ .
\end{equation}

On the other hand, we check directly that $\psi (0) = 0$. This shows
that 0 cannot be a minimizer of $\psi$, not even a local one.
So $\overline{u} \ne 0$ and
$\overline{u} \ne \Lambda_{o}^{-1} (0) = 0$. \qed
\end{proof}
%
\begin{corollary}
Assume $H$ is $C^{2}$ and
$\left(a_{\infty},b_{\infty}\right)$-subquadratic at infinity. Let
$\xi_{1},\allowbreak\dots,\allowbreak\xi_{N}$  be the
equilibria, that is, the solutions of $H' (\xi ) = 0$.
Denote by $\omega_{k}$
the smallest eigenvalue of $H'' \left(\xi_{k}\right)$, and set:
\begin{equation}
  \omega : = {\rm Min\,} \left\{\omega_{1},\dots,\omega_{k}\right\}\ .
\end{equation}
If:
\begin{equation}
  \frac{T}{2\pi} b_{\infty} <
  - E \left[- \frac{T}{2\pi}a_{\infty}\right] <
  \frac{T}{2\pi}\omega
  \label{2eq:three}
\end{equation}
then minimization of $\psi$ yields a non-constant $T$-periodic solution
$\overline{x}$.
\end{corollary}
%

We recall once more that by the integer part $E [\alpha ]$ of
$\alpha \in \bbbr$, we mean the $a\in \bbbz$
such that $a< \alpha \le a+1$. For instance,
if we take $a_{\infty} = 0$, Corollary 2 tells
us that $\overline{x}$ exists and is
non-constant provided that:

\begin{equation}
  \frac{T}{2\pi} b_{\infty} < 1 < \frac{T}{2\pi}
\end{equation}
or
\begin{equation}
  T\in \left(\frac{2\pi}{\omega},\frac{2\pi}{b_{\infty}}\right)\ .
  \label{2eq:four}
\end{equation}

%
\begin{proof}
The spectrum of $\Lambda$ is $\frac{2\pi}{T} \bbbz +a_{\infty}$. The
largest negative eigenvalue $\lambda$ is given by
$\frac{2\pi}{T}k_{o} +a_{\infty}$,
where
\begin{equation}
  \frac{2\pi}{T}k_{o} + a_{\infty} < 0
  \le \frac{2\pi}{T} (k_{o} +1) + a_{\infty}\ .
\end{equation}
Hence:
\begin{equation}
  k_{o} = E \left[- \frac{T}{2\pi} a_{\infty}\right] \ .
\end{equation}

The condition $\gamma < -\lambda < \delta$ now becomes:
\begin{equation}
  b_{\infty} - a_{\infty} <
  - \frac{2\pi}{T} k_{o} -a_{\infty} < \omega -a_{\infty}
\end{equation}
which is precisely condition (\ref{2eq:three}).\qed
\end{proof}
%

\begin{lemma}
Assume that $H$ is $C^{2}$ on $\bbbr^{2n} \setminus \{ 0\}$ and
that $H'' (x)$ is non-de\-gen\-er\-ate for any $x\ne 0$. Then any local
minimizer $\widetilde{x}$ of $\psi$ has minimal period $T$.
\end{lemma}
%
\begin{proof}
We know that $\widetilde{x}$, or
$\widetilde{x} + \xi$ for some constant $\xi
\in \bbbr^{2n}$, is a $T$-periodic solution of the Hamiltonian system:
\begin{equation}
  \dot{x} = JH' (x)\ .
\end{equation}

There is no loss of generality in taking $\xi = 0$. So
$\psi (x) \ge \psi (\widetilde{x} )$
for all $\widetilde{x}$ in some neighbourhood of $x$ in
$W^{1,2} \left(\bbbr / T\bbbz ; \bbbr^{2n}\right)$.

But this index is precisely the index
$i_{T} (\widetilde{x} )$ of the $T$-periodic
solution $\widetilde{x}$ over the interval
$(0,T)$, as defined in Sect.~2.6. So
\begin{equation}
  i_{T} (\widetilde{x} ) = 0\ .
  \label{2eq:five}
\end{equation}

Now if $\widetilde{x}$ has a lower period, $T/k$ say,
we would have, by Corollary 31:
\begin{equation}
  i_{T} (\widetilde{x} ) =
  i_{kT/k}(\widetilde{x} ) \ge
  ki_{T/k} (\widetilde{x} ) + k-1 \ge k-1 \ge 1\ .
\end{equation}

This would contradict (\ref{2eq:five}), and thus cannot happen.\qed
\end{proof}
%
\paragraph{Notes and Comments.}
The results in this section are a
refined version of \cite{2clar:eke};
the minimality result of Proposition
14 was the first of its kind.

To understand the nontriviality conditions, such as the one in formula
(\ref{2eq:four}), one may think of a one-parameter family
$x_{T}$, $T\in \left(2\pi\omega^{-1}, 2\pi b_{\infty}^{-1}\right)$
of periodic solutions, $x_{T} (0) = x_{T} (T)$,
with $x_{T}$ going away to infinity when $T\to 2\pi \omega^{-1}$,
which is the period of the linearized system at 0.

\begin{table}
\caption{This is the example table taken out of {\it The
\TeX{}book,} p.\,246}
\begin{center}
\begin{tabular}{r@{\quad}rl}
\hline
\multicolumn{1}{l}{\rule{0pt}{12pt}
                   Year}&\multicolumn{2}{l}{World population}\\[2pt]
\hline\rule{0pt}{12pt}
8000 B.C.  &     5,000,000& \\
  50 A.D.  &   200,000,000& \\
1650 A.D.  &   500,000,000& \\
1945 A.D.  & 2,300,000,000& \\
1980 A.D.  & 4,400,000,000& \\[2pt]
\hline
\end{tabular}
\end{center}
\end{table}
%
\begin{theorem} [Ghoussoub-Preiss]
Assume $H(t,x)$ is
$(0,\varepsilon )$-subquadratic at
infinity for all $\varepsilon > 0$, and $T$-periodic in $t$
\begin{equation}
  H (t,\cdot )\ \ \ \ \ {\rm is\ convex}\ \ \forall t
\end{equation}
\begin{equation}
  H (\cdot ,x)\ \ \ \ \ {\rm is}\ \ T{\rm -periodic}\ \ \forall x
\end{equation}
\begin{equation}
  H (t,x)\ge n\left(\left\|x\right\|\right)\ \ \ \ \
  {\rm with}\ \ n (s)s^{-1}\to \infty\ \ {\rm as}\ \ s\to \infty
\end{equation}
\begin{equation}
  \forall \varepsilon > 0\ ,\ \ \ \exists c\ :\
  H(t,x) \le \frac{\varepsilon}{2}\left\|x\right\|^{2} + c\ .
\end{equation}

Assume also that $H$ is $C^{2}$, and $H'' (t,x)$ is positive definite
everywhere. Then there is a sequence $x_{k}$, $k\in \bbbn$, of
$kT$-periodic solutions of the system
\begin{equation}
  \dot{x} = JH' (t,x)
\end{equation}
such that, for every $k\in \bbbn$, there is some $p_{o}\in\bbbn$ with:
\begin{equation}
  p\ge p_{o}\Rightarrow x_{pk} \ne x_{k}\ .
\end{equation}
\qed
\end{theorem}
%
\begin{example} [{{\rm External forcing}}]
Consider the system:
\begin{equation}
  \dot{x} = JH' (x) + f(t)
\end{equation}
where the Hamiltonian $H$ is
$\left(0,b_{\infty}\right)$-subquadratic, and the
forcing term is a distribution on the circle:
\begin{equation}
  f = \frac{d}{dt} F + f_{o}\ \ \ \ \
  {\rm with}\ \ F\in L^{2} \left(\bbbr / T\bbbz; \bbbr^{2n}\right)\ ,
\end{equation}
where $f_{o} : = T^{-1}\int_{o}^{T} f (t) dt$. For instance,
\begin{equation}
  f (t) = \sum_{k\in \bbbn} \delta_{k} \xi\ ,
\end{equation}
where $\delta_{k}$ is the Dirac mass at $t= k$ and
$\xi \in \bbbr^{2n}$ is a
constant, fits the prescription. This means that the system
$\dot{x} = JH' (x)$ is being excited by a
series of identical shocks at interval $T$.
\end{example}
%
\begin{definition}
Let $A_{\infty} (t)$ and $B_{\infty} (t)$ be symmetric
operators in $\bbbr^{2n}$, depending continuously on
$t\in [0,T]$, such that
$A_{\infty} (t) \le B_{\infty} (t)$ for all $t$.

A Borelian function
$H: [0,T]\times \bbbr^{2n} \to \bbbr$
is called
$\left(A_{\infty} ,B_{\infty}\right)$-{\it subquadratic at infinity}
if there exists a function $N(t,x)$ such that:
\begin{equation}
  H (t,x) = \frac{1}{2} \left(A_{\infty} (t) x,x\right) + N(t,x)
\end{equation}
\begin{equation}
  \forall t\ ,\ \ \ N(t,x)\ \ \ \ \
  {\rm is\ convex\ with\  respect\  to}\ \ x
\end{equation}
\begin{equation}
  N(t,x) \ge n\left(\left\|x\right\|\right)\ \ \ \ \
  {\rm with}\ \ n(s)s^{-1}\to +\infty\ \ {\rm as}\ \ s\to +\infty
\end{equation}
\begin{equation}
  \exists c\in \bbbr\ :\ \ \ H (t,x) \le
  \frac{1}{2} \left(B_{\infty} (t) x,x\right) + c\ \ \ \forall x\ .
\end{equation}

If $A_{\infty} (t) = a_{\infty} I$ and
$B_{\infty} (t) = b_{\infty} I$, with
$a_{\infty} \le b_{\infty} \in \bbbr$,
we shall say that $H$ is
$\left(a_{\infty},b_{\infty}\right)$-subquadratic
at infinity. As an example, the function
$\left\|x\right\|^{\alpha}$, with
$1\le \alpha < 2$, is $(0,\varepsilon )$-subquadratic at infinity
for every $\varepsilon > 0$. Similarly, the Hamiltonian
\begin{equation}
H (t,x) = \frac{1}{2} k \left\|k\right\|^{2} +\left\|x\right\|^{\alpha}
\end{equation}
is $(k,k+\varepsilon )$-subquadratic for every $\varepsilon > 0$.
Note that, if $k<0$, it is not convex.
\end{definition}
%

\paragraph{Notes and Comments.}
The first results on subharmonics were
obtained by Rabinowitz in \cite{2rab}, who showed the existence of
infinitely many subharmonics both in the subquadratic and superquadratic
case, with suitable growth conditions on $H'$. Again the duality
approach enabled Clarke and Ekeland in \cite{2clar:eke:2} to treat the
same problem in the convex-subquadratic case, with growth conditions on
$H$ only.

Recently, Michalek and Tarantello (see Michalek, R., Tarantello, G.
\cite{2mich:tar} and Tarantello, G. \cite{2tar}) have obtained lower
bound on the number of subharmonics of period $kT$, based on symmetry
considerations and on pinching estimates, as in Sect.~5.2 of this
article.

%
% ---- Bibliography ----
%
\begin{thebibliography}{}
%
\bibitem[1980]{2clar:eke}
Clarke, F., Ekeland, I.:
Nonlinear oscillations and
boundary-value problems for Hamiltonian systems.
Arch. Rat. Mech. Anal. 78, 315--333 (1982)

\bibitem[1981]{2clar:eke:2}
Clarke, F., Ekeland, I.:
Solutions p\'{e}riodiques, du
p\'{e}riode donn\'{e}e, des \'{e}quations hamiltoniennes.
Note CRAS Paris 287, 1013--1015 (1978)

\bibitem[1982]{2mich:tar}
Michalek, R., Tarantello, G.:
Subharmonic solutions with prescribed minimal
period for nonautonomous Hamiltonian systems.
J. Diff. Eq. 72, 28--55 (1988)

\bibitem[1983]{2tar}
Tarantello, G.:
Subharmonic solutions for Hamiltonian
systems via a $\bbbz_{p}$ pseudoindex theory.
Annali di Matematica Pura (to appear)

\bibitem[1985]{2rab}
Rabinowitz, P.:
On subharmonic solutions of a Hamiltonian system.
Comm. Pure Appl. Math. 33, 609--633 (1980)

\end{thebibliography}
\clearpage
\addtocmark[2]{Author Index} % additional numbered TOC entry
\renewcommand{\indexname}{Author Index}
\printindex
\clearpage
\addtocmark[2]{Subject Index} % additional numbered TOC entry
\markboth{Subject Index}{Subject Index}
\renewcommand{\indexname}{Subject Index}
\input{subjidx.ind}
\end{document}

### 2016-11-14 com.tex
the definition of the commitment scheme

\begin{section}{Preliminary on Commitments scheme and Zero Knowledge proof}
	\begin{definition}{\textsf{Commitment}}
	A commitment scheme $\mathsf{COM} = (\KeyGen, \Com, \Verif)$ is a triple of PPT algorithms such that:
	\begin{description}
		\item[$\KeyGen	(1^\lambda) \to \ck$]: The key generation algorithm takes the security parameter $1^\lambda$ in the unary presentation and it outputs the commitment key $\ck$.
		\item[$\Com(\ck, m; \vec{r}) \to \com$]: The commit algorithm takes $\ck$ and the message to be committed $m$, the algorithm draws a random vectors $\vec{r} \sample R$. The algorithm outputs the commitment $\com$ and the openning information $\open$.
		\item[$\Verif(\ck, m, \com, \open) \to \{\True, \False\}$]: This verification takes $\ck$, $m$, $\com$ and $\open$, verifies whether the commitment and the openning information correspond to the message $m$ and the commitment key $\ck$. Then it outputs $\True$ or $\False$.
	\end{description}	
	\end{definition}
\end{section}

\begin{section}{Commitment based on  Ring-SIS~\cite{DBLP:journals/iacr/BaumDOP16}}
	In this section, we will introduce the commitment schem based on Ring-SIS introduced by Baum~\etal~\cite{DBLP:journals/iacr/BaumDOP16}.

	Before the explicite construction, we need to introduce somme notation.

	\begin{definition}{$(D, \gamma_D, d_R)$-commitment friendly ring}

		The ring $R_q = R/qR$ is $(D, \gamma_D, d_R)$-commitment friendly if there is a subset $D \subseteq R$ such that for any $c$

	\end{definition}

	\begin{description}
		\item[$\KeyGen(1^\lambda)$] :

	\end{description}

\end{section}

### 2016-11-18 com.tex
add section about regev encryption

@@
 		\item[$\KeyGen	(1^\lambda) \to \ck$]: The key generation algorithm takes the security parameter $1^\lambda$ in the unary presentation and it outputs the commitment key $\ck$.
-		\item[$\Com(\ck, m; \vec{r}) \to \com$]: The commit algorithm takes $\ck$ and the message to be committed $m$, the algorithm draws a random vectors $\vec{r} \sample R$.
-The algorithm outputs the commitment $\com$ and the openning information $\open$.
-		\item[$\Verif(\ck, m, \com, \open) \to \{\True, \False\}$]: This verification takes $\ck$, $m$, $\com$ and $\open$, verifies whether the commitment and the openning information correspond to the message $m$ and the commitment key $\ck$.
+		\item[$\Com(\ck, m; \vec{r}) \to (\com, \open)$]: The commit algorithm takes $\ck$ and the message to be committed $m$, the algorithm draws a random vectors $\vec{r} \sample R$.
+The algorithm outputs the commitment $\com$ and the opening information $\open$.
+		\item[$\Verif(\ck, m, \com, \open) \to \{\True, \False\}$]: This verification takes $\ck$, $m$, $\com$ and $\open$, verifies whether the commitment and the opening information correspond to the message $m$ and the commitment key $\ck$.
 Then it outputs $\True$ or $\False$.
@@
 	\end{definition}
+
+        \begin{definition}{\textsf{(Binding)}}
+
+        \end{definition}
+
 \end{section}
@@
 \begin{section}{Commitment based on  Ring-SIS~\cite{DBLP:journals/iacr/BaumDOP16}}
-	In this section, we will introduce the commitment schem based on Ring-SIS introduced by Baum~\etal~\cite{DBLP:journals/iacr/BaumDOP16}.
+	In this section, we will introduce the commitment scheme based on Ring-SIS introduced by Baum~\etal~\cite{DBLP:journals/iacr/BaumDOP16}.
 
-	Before the explicite construction, we need to introduce somme notation.
+	Before the explicit construction, we need to introduce some notation.
 
-	\begin{definition}{$(D, \gamma_D, d_R)$-commitment friendly ring}
+	\begin{definition}{$(D, \gamma_D, d_R)$-commitment friendly ring~\cite{DBLP:journals/iacr/BaumDOP16}}
 
-		The ring $R_q = R/qR$ is $(D, \gamma_D, d_R)$-commitment friendly if there is a subset $D \subseteq R$ such that for any $c$
+		The ring $R_q = R/qR$ is $(D, \gamma_D, d_R)$-commitment friendly if there is a subset $D \subseteq R$ such that for any $c \in D$ and $r \in R$ with $deg(r) < 2d_R$, we have $||c \cdot r ||_{\infty} \leq \gamma_D||r||_{\infty}$.
+Furthermore, for any $d, d' \in D$ it holds that $d- d'$ is invertible modulo $q$, and $deg(d)< d_R$
 
@@
 
+        We present the a commitment scheme which is computationally binding and statistically hinding commitment
+
+        \begin{construction}{Ring-SIS based commitment}
+
           \begin{description}
-		\item[$\KeyGen(1^\lambda)$] :
+          \item[$\KeyGen(1^\lambda) \to \ck$]: Output $(D, \gamma_D, d_R)$-commitment friendly ring $R_q$, a uniformly random matrix $A \in R_q^{(k+1) \times m}$, constants $\gamma > 1$ and $\beta$ such that $\gamma Nm\beta \gamma_D^2 < q$, and a distribution $\mathcal{D}$ that will output vectors in $R^m$.
+It is required that any vector that can be produced with non-zero probability has norm at most $\beta$ and degree less that $d_R$.
+
+          \item[$\Com(\ck, m; \vec{r})) \to (\com, \open)$]: To commit a message $m\in R_q^k$, we draw a random vector $\vec{r} \sample R^m$ accroding to the distribution $\mathcal{D}$ ($||r||_{\infty} \leq \beta$ and $deg(\vec{r} < d_R)$), the commitment will be computed as:
+            \begin{align*}
+              \Com(\vec{m}; \vec{r}) &:= A\vec{r} + \left( \begin{matrix} 0 \\ \vec{m} \end{matrix} \right)\\
+              \open &:= (\vec{r}, f\in D)
+            \end{align*}
+
+          \item[$\Verif(\ck, m, \com, \open) \to \{\True, \False\}$]: The verification algrotihm checks:
+            \begin{align*}
+              A\vec{r} + \left( \begin{matrix} 0 \\ f\vec{x} \end{matrix}\right) &= f\vec{c}
+            \end{align*}
+
+            and that $||\vec{r}||_\infty \leq \gamma N m \beta \gamma_D$ and $deg(\vec{r}) < 2 d_R$.
 
           \end{description}
+        \end{construction}
+        \begin{proof}
+
+        \end{proof}
 

### 2016-11-18 draft.tex
add section about regev encryption

%\begin{section}{One-time linearly homomorphic signature based on the Ring-SIS problem}
% 
%This idea comes from the one-time signature based on the Ring-SIS problem proposed by Lyubashevsky and Micciancio~\cite{DBLP:conf/tcc/LyubashevskyM08}.
% 
%\begin{construction}{$R$-SIS based one-time linearly homomorphic signature}
% 
%  \begin{description}
%  \item[$\Setup(1^\lambda) \to (\SSK, \SVK)$] :
%    \begin{enumerate}
%    \item We specify the ring-SIS problem for the degree-$n$ ring $R$ over $\mathbb{Z}$. The security of the one-time signature scheme is based on the $R$-SIS problem.
%    \item Take $\ell \approx log(q)$. We draw a random vector $\vec{a} \sample R_q^{\ell}$.
%    \item Then we draw a matrix $X$ composed by small coefficients in the ring $R_q$.
%    \item Compute $f_{\vec{a}}(X) = \vec{a}^{T} \cdot X$.
%    \end{enumerate}
%  \end{description}
%\end{construction}
% 
%\end{section}

### 2016-11-18 enc.tex
add section about regev encryption

As one of the most important cryptographic primitive, the encryption scheme is studied for decades. In this section, we will present some lattice based encryption scheme.

\begin{section}{Regev and Dual-Regev LWE-based encryption scheme}

The Regev's LWE encryption~\cite{DBLP:conf/stoc/Regev05} scheme is the first LWE based encryption scheme.

\begin{construction}{Regev's encryption scheme}
  The Regev's encryption scheme is a triple of PPT algorithm $(\KeyGen, \Enc, \Dec)$.
  \begin{description}
  \item[$\KeyGen(1^\lambda) \to (\SK, \PK)$]: 
    \begin{enumerate}
    \item We draw a uniformly random vector $\vec{s} \in \mathbb{Z}_q^n$ and set it the secret key for the encryption scheme.
    \item Draw a random vector $\vec{e} \in \mathbb{Z}_q^m$ \wrt the distribution $\chi$ and a uniformaly random matrix $\tilde{A} \in \mathbb{Z}_q^{n \times m}$ for $m \approx (n+1) log(q)$. Then the algorithm computes $\vec{b} = \vec{s}^T \cdot \tilde{A} + \vec{e}^T~mod~q$.
    \item Compute the matrix $A$ as follows:
      \begin{align*}
        A &= \left[ \begin{matrix} ~\tilde{A}~ \\ ~\vec{b}^T~ \end{matrix} \right] \in \mathbb{Z}_q^{(n+1) \times m}.
      \end{align*}
    \item Note that we have the following information:
      \begin{align*}
        (-\vec{s}^T, 1) \cdot A = \vec{e}^T &\approx \vec{0} (mod~ q).
      \end{align*}
    \end{enumerate}
  \end{description}
\end{construction}

\end{section}

### 2016-11-18 zkpok.tex
add section about regev encryption

\begin{section}{Ring-SIS based Zero-Knowledge proof system}
  In this section, we present the Ring-SIS based Zero-Knowledg proof system, which is described initially in the paper~\cite{DBLP:journals/iacr/BaumDOP16}.
  It's based on this $\Sigma$ protocol, we construct the our Designed Verifier Zero-Knowledge proof system.

  \begin{construction}{$\Sigma$-protocol for Opening a Commitment $\Pi_{\open}$}

    In this proof scheme, we proof the plaintext knowledge $x$ corresponded to the committed value $\vec{c} = C(x; \vec{r})$.

    \begin{enumerate}
    \item The prover computes a commitment $\vec{t} = C(\mu; \vec{\rho})$, here $\mu$ and $\vec{\rho}$ are chosen uniformly form $R_q$ and $R^m$. 
      And rejection sampling on the fact that $||\vec{\rho}||_{infty} \leq (1+ \frac{\gamma N m}{2}) \beta \gamma_D$ and $deg(\vec{\rho}) < 2 d_R$.
    \item The verifier sends a random challenge $d \in D$.
    \item The prover's goal in this stage is try to open the commitment $\vec{t} + t\vec{c}$ \wrt the opening information $\vec{r}_z = \vec{\rho} + d\vec{r}$.
      The protocol abort if we have $||\vec{r}_z||_{\infty} > \frac{\gamma N m}{2} \cdot \beta \gamma_D$. 
      If the algorithm has not aborted, the prover sends $z, \vec{r}_z$ and the opening information $\open_{aux}$ \wrt the commitment $\vec{c}_{aux}$ to the verifier.
    \item The verifier checks the opening information $\open_{aux}$ is valid, $C(z; \vec{z}_r) = \vec{t} + d \vec{c}$
      and also the random vector $\vec{r}_z$ verifies that $||\vec{r}_z||_{infty} \leq ||\frac{\gamma N m}{2} \cdot \beta \gamma_D||$ and $deg(\vec{r}_z) < 2d_R$.
    \end{enumerate}
  \end{construction}

\end{section}

\begin{section}{Transformation form the $\Sigma$-protocol to Designed Verifier Zero-Knowledge proof system}

  The transformation is applied for a special family of $\Sigma$-protocol.

\end{section}

### 2016-11-25 draft.tex
add the draft construction on dvnizk
friday 25 11 2016 begin of the fhe description

@@
 %\end{section}
+\begin{section}{Fully homomorphic encryption scheme}
+  In this section we present several fully homomorphic encryption scheme.
+
+  \begin{subsection}{Third generation of fully homomoprhic encryption scheme}
+
+    Here we present the third generation of fully homomorphic encryption scheme~\cite{DBLP:conf/crypto/GentrySW13}.
+
+    At first, we discribe the basic encryption scheme without the homomorphic encryption.
+
+    \begin{description}
+    \item[$\boldmath{\Setup(1^\lambda, 1^L)}$]:
+      \begin{enumerate}
+      \item a
+      \end{enumerate}
+
+    \end{description}
+  \end{subsection}
+
+\end{section}
+
+\begin{section}{Designed Verifier Non-Interactive proof system}
+
+  Our scheme based on the $\Sigma$-protocol proposed by Baum~\etal~\cite{DBLP:journals/iacr/BaumDOP16} and we instantiate the transformation from $\Sigma$-protocol to $NIZK$ without random oracle~\cite{DBLP:conf/pkc/ChaidosG15}.
+
+  \begin{subsection}{$\Sigma$-protocol for encryption of $0$ or $1$}
+    In this subsection, we will try to instantiate the $\Sigma$-protocol for encryption of $0$ or $1$ with the lattice assumptions.
+    And try to proof the soundness with unique identifiable challenge property for a such $\Sigma$-protocol.
+
+    \begin{description}
+      \item[$\Prove((ek,c), (m,r), (m, r))$]:
+
+    \end{description}
+
+  \end{subsection}
+
+  \begin{subsection}{$DVNIZK$ for the correct committed value}
+
+    In this section we will give an instantiation of the sigma protocol  for encryption of $0$ or $1$ by Regev's encryption scheme.
+
+    \begin{description}
+
+    \item[$\Setup(1^\lambda)$]:
+
+      \begin{enumerate}
+      \item We draw a random matrix $A \in R_q^{n\times m}$ and a vector $\vec{s} \in R_q^{m \times 1}$.
+      \end{enumerate}
+    \end{description}
+  \end{subsection}
+
+\end{section}

### 2016-11-25 fhe.tex
friday 25 11 2016 begin of the fhe description

\begin{section}{Fully homomorphic encryption scheme~\cite{DBLP:conf/crypto/GentrySW13}}

  In this section, we will instantiate the GSW fully homomorphic encryption scheme.

  As in the original paper, we will firstly give a basic encryption scheme.

  \begin{desciption}
  \item[$\Setup(1^\lambda)$]: 
    \begin{enumerate}
    \item We
    \end{enumerate}
  \end{description}

\end{section}

### 2016-12-28 LTF.tex
modif 28/12/2016 day

Lossy trapdoor functions are proved to be very usefull for the construction of CCA-secure encryption scheme. 
There already exists many efficient constructions of all-but-one lossy trapdoor functions with various assumptions~\cite{DBLP:journals/siamcomp/PeikertW11, DBLP:conf/crypto/BoldyrevaFO08}

\begin{section}{All-but-one lossy trapdoor function}

\end{section}

### 2016-12-28 assump.tex
modif 28/12/2016 day

In this chapter, we give the definitions of various lattice assumptions.

\begin{section}{Notations and prelimaries}
  \begin{definition}{(Gaussian Distribution)}
    We define the continous Normal Distribution on $\mathbb{R}^m$ centered at $\vec{v}$ with standard deviation $\sigma$ by the density function $\rho_{\vec{v}, \sigma}^m(\vec{x}) =  (\sqrt{2\pi} \sigma)^{-m}exp(-\frac{||\vec{x} - \vec{v}||^2}{2 \sigma^2})$. For the simplicity of the notations, we avoid the subscript $\vec{v}$ if $\vec{v} = 0^m$.

    The discrete Normal Distribution on $\mathbb{Z}^m$ centered at $\vec{v}$ with standard deviation $\sigma$ is defined by the density function $D_{\vec{v}, \sigma}^{m}(\vec{x}) =  \rho_{\vec{v}, \sigma}^m(\vec{x})/ \rho_{\sigma}(\mathbb{Z}^m)$, where $\rho_{sigma}(\mathbb{Z}^m) = \Sigma_{z \in \mathbb{Z}^m} = \rho_{\sigma}^{m}(\vec{z})$ is the scaling factor required to obtain a probability distribution.
  \end{definition}

  The rejection sampling informally states that if $\sigma \in \tilde{\Theta}(||\vec{v}||)$, then the rejection sampling procedure will result in a distriution statistically close to $D_{\sigma}^\ell$ which is independent from the vector $\vec{v}$. The pro0cedure only requires a constant number of iterations. For the concrete parameters we refer to the original work of Lyubashevsky~\cite{DBLP:conf/eurocrypt/Lyubashevsky12}.

  \begin{definition}{(Rejection Sampling)}

    Let $V$ be a subset of $\mathbb{Z}^{\ell}$ in which all elements have norms less that $T$ and let $h$ be a probability distribution over $V$. Then for any constant $M$, there exists a $\sigma = \tilde{\Theta}(T)$ such that the output distribution of the following algorithms $A, F$ are statistically close:

    A:
    \begin{enumerate}
    \item $\vec{v} \sample h$.
    \item $\vec{z} \sample D_{\vec{v}, \sigma}^\ell$.
    \item Output $(\vec{z}, \vec{v})$ with probability $min(exp(\frac{-2\langle\vec{z}, \vec{v}\rangle + ||\vec{v}||^2}{2 \sigma^2}),1)$.
    \end{enumerate}

    F:
    \begin{enumerate}
    \item $\vec{v} \sample h$.
    \item $\vec{z} \sample D_{\sigma}^\ell$.
      \item Output $(\vec{z}, \vec{v})$ with probability $\frac{1}{M}$.
    \end{enumerate}

    Remark that $M$ is independent from the vector $\vec{v}$.

  \end{definition}

\end{section}

\begin{section}{Hardness assumptions}

  \begin{definition}{(Ring-LWE)}
    Let $R = \mathbb{Z}[x] /\langle x^n +1\rangle$, $R_q = R/ qR$ and $\chi$ be a distribution over $R$.
    The decisional ring learning with errors assumption (denoted by $RLWE_{q, \chi}$) states that:
    \begin{align*}
      \{ (a_i, a_i \cdot s + e_i)\} &\approx_c \{(a_i, u_i)\},
    \end{align*}
    for any polynomial number of samples, where $a_i \sample R_q$, $e_i \sample \chi$, $u_i \sample R_q$ and $s \sample R_q$.
  \end{definition}

\end{section}

### 2016-12-28 fhe.tex
modif 28/12/2016 day

@@
-\begin{section}{Fully homomorphic encryption scheme~\cite{DBLP:conf/crypto/GentrySW13}}
-
-  In this section, we will instantiate the GSW fully homomorphic encryption scheme.
+In this section, we will instantiate the fully homomorphic encryption scheme of third generation\cite{DBLP:conf/crypto/GentrySW13}.
 
@@
 
-  \begin{desciption}
-  \item[$\Setup(1^\lambda)$]: 
+The entire FHE homomorphic encryption scheme is a $6$-tuple of PPT algorithm 
+$$FHE = (\Setup, \SKGen, \PKGen, \Enc, \Dec, \MPDec).$$ 
+For the clarity, we separate the parameters generation algorithm into three parts.
+
+\begin{section}{Notations and simple properties}
+  \begin{definition}{Bit Decomposition, Powers of $2$ and Flatten algorithms}
+    For $q$ a prime of $\ell+1$ bits, we specify the following three algorithms: $(\BitDecomp, \Powers, \Flatten)$ as follows.
+    \begin{description}
+    \item[${\mathsf{\BitDecomp}}: \mathbb{Z}_q^{n} \to \{0,1\}^{(\ell+1) \times n}$]
+      \begin{align*}
+        \BitDecomp(\vec{v} = [v_0, v_1, \dots, v_{n-1}]) &= [v_{0,0}, \dots v_{0,\ell}, v_{1,0}, \dots v_{n-1,0}, \dots, v_{n-1, \ell}]
+      \end{align*}
+      where $v_{i,j}$ represents the $j$-th bit of the $i$-th coefficient of the vector $\vec{v}$.
+
+    \item[${\mathsf{\Powers}}: \mathbb{Z}_q^{n} \to \mathbb{Z}_q^{(\ell+1) \times n}$]
+      \begin{align*}
+        \Powers(\vec{v} = [v_0, v_1, \dots, v_{n-1}]) &= [v_0, 2 \cdot v_0, \dots 2^{\ell} \cdot v_0, \dots, v_{n-1}, \dots, 2^{n-1} \cdot v_{n-1}]
+      \end{align*}
+
+    \item[${\mathsf{\BitDecomp^{-1}}}: \mathbb{Z}_q^{1 \times ((n + 1) \times \ell)} \to \mathbb{Z}_q^{\ell+1}$]
+      \begin{align*}
+        \BitDecomp(\hat{\vec{v}} = [v_{0,0}, \dots v_{0,\ell}, v_{1,0}, \dots v_{n-1,0}, \dots, v_{n-1, \ell}]) &= [v_0, v_1, \dots, v_{n-1}]\\
+                                                                                                               &=[\sum_{i = 0}^{\ell} v_{0,i}, \dots, \sum_{i=0}^{\ell} v_{n-1, i}]
+      \end{align*}
+
+      We notice that the input of the function ${\mathsf{\BitDecomp}^{-1}}$ can be not only the bits but the elements in the ring $\mathbb{Z}_q$.
+With this remark, we construct the following function $\Flatten$ which transforms a vector of "bits" in $\mathbb{Z}_q$ into a vector of real bits.
+
+    \item[$\Flatten: \mathbb{Z}_q^{1 \times ((n + 1) \times \ell)} \to \{0,1\}^{(\ell+1) \times n}$]
+      \begin{align*}
+        \Flatten(\hat{\vec{v}}) &= \BitDecomp( \BitDecomp^{-1}(\hat{\vec{v}}))
+      \end{align*}
+
+    \end{description}
+
+    Remark that each function has his matrix version which simply applies the function to each row of the matrix.
+  \end{definition}
+
+  Here we will prove some useful properties of the functions
+
+  \begin{lemma}{Linearity of Flatten}
+
+    For $\hat{\vec{a}}, \hat{\vec{b}} \in \mathbb{Z}_q^{1 \times ((\ell+1) \times n)}$ and $\lambda \in \mathbb{Z}_q$ we have the following equality:
+    \begin{align*}
+      \Flatten(\Flatten(\hat{\vec{a}}) + \Flatten(\hat{\vec{b}})) &= \Flatten(\hat{\vec{a}}+ \hat{\vec{b}})
+    \end{align*}
+
+  \end{lemma}
+
+  \begin{proof}
+
+    Note the different variables as follows:
+
+    \begin{align*}
+      \hat{\vec{a}} &= [\hat{a}_{0,0}, \dots, \hat{a}_{0, \ell}, \dots, \hat{a}_{n-1, 0}, \dots, \hat{a}_{n-1, \ell}] & \hat{\vec{b}} &= [\hat{b}_{0,0}, \dots, \hat{b}_{0, \ell}, \dots, \hat{b}_{n-1, 0}, \dots, \hat{b}_{n-1, \ell}]\\
+      a_{j} &= \sum_{i = 0}^{\ell}\hat{a}_{j, i}~(mod~q) & b_{j} &= \sum_{i = 0}^{\ell} \hat{b}_{j, i}~(mod~q)\\
+      \vec{a} &= \Flatten(\hat{\vec{a}})\\
+                    &= [a_{0,0}, \dots, a_{0, \ell}, \dots, a_{n-1, 0}, \dots, a_{n-1, \ell}]\\
+      \vec{b} &= \Flatten(\hat{\vec{b}})\\
+                    &= [b_{0,0}, \dots, b_{0, \ell}, \dots, b_{n-1, 0}, \dots, b_{n-1, \ell}]
+    \end{align*}
+
+    We remark that
+    \begin{align*}
+      a_{j} &= \sum_{i = 0}^{\ell}\hat{a}_{j, i}~(mod~q) & b_{j} &= \sum_{i = 0}^{\ell} \hat{b}_{j, i}~(mod~q)\\
+      &= \sum_{i = 0}^{\ell}a_{j, i}~(mod~q) & &= \sum_{i = 0}^{\ell} b_{j, i}~(mod~q)\\
+    \end{align*}
+
+    which means exactly
+    \begin{align*}
+      \BitDecomp^{-1}(\Flatten(\hat{\vec{a}}) + \Flatten(\hat{\vec{b}})) &= \BitDecomp^{-1}(\hat{\vec{a}}+ \hat{\vec{b}})
+    \end{align*}
+
+    Thus we have
+    \begin{align*}
+      \Flatten(\Flatten(\hat{\vec{a}}) + \Flatten(\hat{\vec{b}})) &= \Flatten(\hat{\vec{a}}+ \hat{\vec{b}})
+    \end{align*}
+
+  \end{proof}
+
+  \begin{lemma}\label{rm-flatten}
+    For prime number $q$ and $m \in \mathbb{Z}_q$, we have the following equality:
+    \begin{align*}
+      \Flatten(m \cdot I_N) \cdot \left( \begin{smallmatrix} 1\\ 2\\ \vdots\\ 2^{l-1}  \end{smallmatrix}\right) &= m \cdot \left( \begin{smallmatrix} 1\\ 2\\ \vdots\\ 2^{l-1}  \end{smallmatrix}\right) ~mod~q
+    \end{align*}
+  \end{lemma}
+
+\end{section}
+
+\begin{section}{Construction of GSW fully homomorphic encryption scheme}
+
+  \begin{description}
+  \item[$\Setup(1^\lambda, 1^L)$]:
+
+    We generate the parameters
+
     \begin{enumerate}
-    \item We
+    \item Choose a modulus $q$ of $\kappa = \kappa(\lambda, L)$ bits, the lattice dimension parameter $n = n (\lambda, L)$ and the error distribution $\chi = \chi(\lambda, L)$ to ensure at least $\lambda$ bit security against the LWE problem.
+    \item Then we compute $m = m (\lambda, L) = O (n~log~q)$, $\ell = \floor{q} + 1$ and $N = (\ell + 1) \times n$
+    \item Output $PP = (n, q, \chi, m)$.
+    \end{enumerate}
+
+  \item[$\SKGen(\PP)$]:
+    \begin{enumerate}
+    \item Sample $\vec{t} \sample \mathbb{Z}_q^m$.
+    \item Let $\vec{s} = (1, -t_1, \dots, -t_n) \in \mathbb{Z}_q^{n+1}$.
+    \item Output the secret key $\SK = \vec{s}$.
+    \end{enumerate}
+
+  \item[$\PKGen(\PP, \SK)$]:
+    \begin{enumerate}
+    \item Parse $\SK$ as $\vec{s} = (1 | \vec{t})$.
+    \item Sample a uniformly random matrix $B  \gets \mathbb{Z}_q^{m\times n}$ and a noise vector $\vec{e} \gets \chi^{m}$.
+    \item Compute $\vec{b} = B \cdot \vec{t} + \vec{e}$. 
+    \item Set the matrix $A = [\vec{b} | B ] \in \mathbb{Z}_q^{m \times (n+1)}$, remark that $A \cdot \vec{s} = \vec{e}$.
+    \item Output the public key $\PK = A$.
+    \end{enumerate}
+
+  \item[$\Enc(\PP, \PK, \mu)$]:
+
+    To encrypt a message $\mu \in \mathbb{Z}_q$.
+    \begin{enumerate}
+    \item Sample a uniform binary matrix $R \in \{0,1\}^{(\ell-1) \times m}$.
+    \item Compute the corresponded ciphertext as bellow:
+      \begin{align*}
+        C &= \Flatten(\mu \cdot [Id_{l-1}| 0] + \BitDecomp(R \cdot A)) \in \mathbb{Z}_q^{(\ell-1) \times N}
+      \end{align*}
+    \item Output the ciphertext $C$.
+    \end{enumerate}
+
+  \item[$\Dec(\PP, \SK, C)$]:
+
+    The decryption algorithm has two version $\Dec$ and $\MPDec$, the first is the basic encryption of one bit $\mu \in \{0,1\}$ and $\MPDec$ is an algorithm from~\cite{DBLP:conf/eurocrypt/MicciancioP12} which can decrypt the message in $\mathbb{Z}_p$.
+    \begin{enumerate}
+    \item We observe that the first $\ell$ coefficients of the vector $\vec{v}$ are $1, 2, \dots , 2^{\ell-1}$.
+    \item Let $i \in \{0,1, \dots \ell-1\}$ such that $v_i \in (q/4, q/2]$. Let $C_i$ be the $i$-th row of $C$.
+    \item Compute $x_i \gets <C_i, \vec{v}>$.
+    \item Output $\mu' = \round{x_i/v_i}$.
+    \end{enumerate}
+
+  \item[$\MPDec(\PP, \SK, C)$]:
+
+    This is the second version of the decryption scheme.
+Here we suppose that $q = 2^{l-1}$, thus the first $\ell - 1$ coefficients  of $\vec{v}$ are $1, 2, \dots, 2^{l-2}$.
+Notice that we have $C \cdot \vec{v} = \mu \cdot \vec{1, 2, \dots, 2^{\ell-2}} + \BitDecomp(R \cdot \vec{e})$ and the second part of the addition is very small (at most $N \times ||\vec{e}||_1$).
+    \begin{enumerate}
+    \item Compute $C \cdot \vec{v} = \mu \cdot \vec{(1, 2, \dots, 2^{\ell-2})} + \BitDecomp(R \cdot \vec{e})$.
+    \item Recover $LSB(\mu)$ from $\mu \cdot 2^{\ell-2} + small$.
+    \item Continue to compute the next-least-significant-bit with $(\mu - LSB(\mu)) \cdot 2^{\ell-3} + small$~\etc.
     \end{enumerate}
@@
 
+  Remark that for general $q$ case, we can use the Nearest Plane algorithm~\cite{DBLP:journals/combinatorica/Babai86} which allow us to remove the noise part in $C \cdot \vec{v}$ and to get the message.
+
+  We also present here the homomorphic operation on the ciphertexts
+  \begin{description}
+  \item[${\mathsf{MultConst}}(C, \alpha)$]: For a ciphertext $C \in \mathbb{Z}_q^{(\ell-1)\times N}$ of the plaintext $m \in \mathbb{Z}_q$ and $\alpha \in \mathbb{Z}_q$, this algorithm generate the new ciphertext $C_\alpha$ corresponded to the message $\alpha \times m$.
+    \begin{enumerate}
+    \item Compute $M_\alpha \gets \Flatten(\alpha \cdot Id_{(\ell-1) \times N})$
+    \item Generate the new ciphertext $C_\alpha \gets \Flatten(M_\alpha \cdot C)$. Note that we have:\
+      \begin{align*}
+        {\mathsf{MultConst}(C, \alpha)} \cdot \vec{v} &= M_\alpha \cdot C \cdot \vec{v}\\
+                                                      &= M_\alpha \cdot (\mu \cdot \vec{v} + \vec{e})\\
+                                                      &= \mu \cdot (M_\alpha \cdot \vec{v}) + M_\alpha \cdot \vec{e}\\
+                                                      &= \alpha \cdot \mu \cdot \vec{v} + M_\alpha \cdot \vec{e}
+      \end{align*}
+    \item Notice that $M_\alpha = \Flatten(\alpha \cdot Id_{(\ell-1) \times N}) = \BitDecomp(\BitDecomp^{-1}(\alpha \cdot Id_{(\ell-1) \times N}))$, thus we have $M_\alpha \in \{0,1\}^{N \times N}$.
+As consequences, the error term of the encryption just grow at most $N$.
+    \end{enumerate}
+
+  \item[${\mathsf{Add}}(C_1, C_2)$]:
+    The addition operation is directly $\Flatten(C_1 + C_2)$. The correctness of the new ciphertext and the bound of the error term in the new ciphertext is straightforward.
+  \end{description}
+
 \end{section}

### 2016-12-28 lemma.tex
modif 28/12/2016 day

\begin{section}{Polynomial theorems}

  \begin{lemma}~\cite{DBLP:conf/asiacrypt/Lyubashevsky16}
    For any polynomial $a \in \mathbb{Z}[x]$ of degree $n$ and a polynomial $b \in \mathbb{Z}[x]$ of degree $m$ each of whose coefficient is chosen at random modulo $q$.
    Let $c$ be the product of the two polynomials $c = a \cdot b$.
    \begin{align*}
    c &= c_0 + c_1 x + \cdots + c_n x^n + \cdots + c_{m+n}x^{m+n}
    \end{align*}

    The coefficients $c_n, \dots, c_{m+n}$ are jointly univormly random modulo q \wrt the polynomial $a$.
  \end{lemma}

\end{section}

### 2017-01-16 assump.tex
modif 01/16/2017

@@
   \begin{definition}{(Ring-LWE)}
-    Let $R = \mathbb{Z}[x] /\langle x^n +1\rangle$, $R_q = R/ qR$ and $\chi$ be a distribution over $R$.
-    The decisional ring learning with errors assumption (denoted by $RLWE_{q, \chi}$) states that:
+    The $\vec{f}$-LWE problem can be defined as follows.
+    Let $R = \mathbb{Z}[x] /\langle \vec{f}\rangle$, $R_q = R/ qR$ and $\chi$ be a distribution over $R$.
+    The decisional ring learning with errors assumption (denoted by $\vec{f}-RLWE_{q, \chi}$) states that:
     \begin{align*}
@@
 
+  \begin{definition}{(Ring-SIS)}
+    The $\vec{f}$-SIS problem can be defined as follows.
+    Let $R = \mathbb{Z}[x] /\langle \vec{f}\rangle$ and $R_q = R/ qR$.
+    The ring small integer solution problem (denoted by $\vec{f}-RSIS_{k, q, \beta}$) states that find a solution $(\vec{z}_1, \dots, \vec{z}_k) \in R_q$ and $||\vec{z}_i|| \leq \beta$ of the following problem is hard:
+    \begin{align*}
+      \sum_{i= 1}^k \vec{a}_i \vec{z}_i &= \vec{0}~mod~\vec{f}
+    \end{align*}
+    for any polynomial number of samples, where $\vec{a}_i \sample R_q$
+  \end{definition}
+
 \end{section}

### 2017-03-03 LTF.tex
add trapdoor functions

@@
 Lossy trapdoor functions are proved to be very usefull for the construction of CCA-secure encryption scheme. 
-There already exists many efficient constructions of all-but-one lossy trapdoor functions with various assumptions~\cite{DBLP:journals/siamcomp/PeikertW11, DBLP:conf/crypto/BoldyrevaFO08}
+There already exists many efficient constructions of all-but-one lossy trapdoor functions with various assumptions~\cite{DBLP:journals/siamcomp/PeikertW11, DBLP:conf/crypto/BoldyrevaFO08}.
+
+The main idea of the lossy trapdoor function is that, it can be operated in two modes: Injective mode and lossy mode.
 
@@
 
+  \begin{definition}
+    A lossy trapdoor function $LTF$ with domain $Dom$ consits of the following algorithms $LTF = (\KeyGen, \Eval, \Inv, \LKeyGen)$:
+    \begin{description}
+    \item[${\mathsf{\KeyGen}}$] :
+      \begin{enumerate}
+        \item $LTF.\KeyGen(1^\lambda)$
+      \end{enumerate}
+    \item[${\mathsf{\Eval}}$] :
+    \item[${\mathsf{\Inv}}$] :
+    \item[${\mathsf{\LKeyGen}}$] :
+    \end{description}
+  \end{definition}
 \end{section}

### 2017-03-03 draftNEFHE.tex
add trapdoor functions

\begin{section}{Non-error Somewhat Fully Homomorphic encryption scheme}
  Here we firstly give the blueprint and the main idea of our construction, This idea is initialized by the work of Fully homomorphic encryption scheme for $NC^1$, which give us a fully homomorphic encryption scheme without error, but using only an mod $2$ additively homomorphic encryption scheme. However, in their work the ciphertext size is doubling when we perform a homomorphic operation on the ciphertext.
  \begin{itemize}
  \item 
  \end{itemize}
\end{section}
